A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
little tweaks in related work

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments ~\cite{bellotti1993design} and evaluating ubiquitous computing applications ~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model ~\cite{hong2004privacy} and a social-based model ~\cite{jiang2002approximate}.

@@

\subsection{Smartphones and Wearables Concerns}
Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones ~\cite{chin2012measuring}, observe behaviors of new smartphone users ~\cite{palen2000going}, investigate user understanding of permissions ~\cite{felt2012android}.

>>>>

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.

@@

\subsection{Smartphones and Wearables Concerns}
Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.
